%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry %Lead R\&D
    {Creative Technology Architect: C++ 17, Unreal Engine 5, Mixed Reality} % Job title
    {Siili Solutions / Epic Games} % Organization
    {Wrocław, Poland} % Location
    {Mar. 2023 - Present} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            Leading a creative project of constructing a HMI Mixed Reality simulator. Defined architecture for the whole system, constructed the physical XR Buck with real vehicle parts and connected it to the virtual world using the Varjo XR-3 headset. Various 3D rendering engines and frameworks were used in production, including Unreal Engine 5, Rightware Kanzi and IPG CarMaker.
        \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer: C++ 17, Qt, QML, Embedded systems} % Job title
    {Siili Solutions / Rimac Automobili} % Organization
    {Wrocław, Poland} % Location
    {Aug. 2021 - Feb. 2023} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            Infotainment HMI development with Qt/QML and C++17 standard. Involved in creation of UI as well as middleware during all of the software life cycle. Was setting up and maintaining an embedded Toradex i.MX 8 based hardware. Created an advanced video playback module using GStreamer and gained automotive and FuSa know-how.
        \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer: C++ 17, Qt, QWidgets, UI design, Embedded systems} % Job title
    {Sii Poland / QIAGEN} % Organization
    {Wrocław, Poland} % Location
    {Nov. 2018 - Jul. 2021} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            Member of a core team developing UI and control software for a new automated end-to-end DNA/RNA purification instrument using Qt/QWidgets and C++17 standard. Obtained knowledge in molecular diagnostics, medical biology and digital electronics. Worked close to the Toradex i.MX 6 based hardware by mounting stepper motor encoders, soldering test hardware board and processing digital signals.
        \end{cvitems}
      % \begin{cvitems} % Description(s) of tasks/responsibilities
      %   \item {Member of a core team developing UI and control software for a new automated DNA/RNA purification instrument.}
      %   \item {Qt Framework and C++17 standard were used in production.}
      %   \item {Obtained knowledge in molecular diagnostics, medical biology and digital electronics.}
      % \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer: C++ 11/14, Python, Node.js, Embedded systems} % Job title
    {Nokia Networks} % Organization
    {Wrocław, Poland} % Location
    {Jul. 2014 - Jan. 2018} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            Developed embedded functionalities for base transceiver stations (BTS) using newest language standards C++11/14. Cooperated with other development, testing and integration teams in a vast multinational environment in Scrum methodology. Possessed knowledge regarding radio technology with its 2G/3G/4G (GSM, WCDMA, LTE) standards.
        \end{cvitems}
      % \begin{cvitems} % Description(s) of tasks/responsibilities
      %   \item {Developed embedded functionalities and code maintenance for base transceiver stations (BTS).}
      %   \item {Participated in multiple projects regarding backend software development in C++ using newest language standards C++11/14.}
      %   \item {Cooperated with other development, testing and integration teams in a vast multi-national environment in Scrum methodology.}
      %   \item {One of the projects required backend services development in JavaScript using Node.js and scripting in Python.}
      %   \item {Possessed knowledge regarding radio technology with its 2G/3G/4G (GSM, WCDMA, LTE) standards.}
      % \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
